Untitled

### 2023-12-30 code/analysis_Redo.Rmd
bit of exploration

did2s(
      data = dfc %>% mutate(outcome = log(Total / Staff)) %>% filter(outcome < 8 & !is.infinite(outcome)), 
      yname = "outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )

@@

>>>>

did2s(
      data = dfc %>% mutate(outcome = log(ngla_revenue / Staff)) %>% filter(outcome < 15 & !is.infinite(outcome)), 
      yname = "outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )

@@

hist(log(dfc$ngla_revenue / dfc$Staff))
summary(log(dfc$ngla_revenue / dfc$Staff))
